A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-02-12 doc/draft-01-stokes/02prelim.tex
update proof or rellich's lemma

>>>>

By the analyticity of $\Gbh$, a consequence of \cref{thrm:rep-theorem}
is
\begin{cor}
\label{cor:analytic}  
  Let $(\uu,p) \in A(\Omega)$ be a solution of \cref{eq:ostokes}.
  Then each component of $\uu(\xx)$ is an analytic function
  of the coordinates $\xx$.
\end{cor}

The proof of \cref{cor:analytic} follows the same reasoning as
that for the Helmholtz case; see \cite[Theorem 3.5]{colton1983integral}.
